2024 US Presidential Election Forecast Model

### 2024-10-22 paper/paper.qmd
update paper.qmd

### Model justification
```{r}
#| echo: false
#| warning: false
#| message: false
model <- lm(pct ~ pollscore + sample_size + numeric_grade, data = raw_data)
summary(model)
```

>>>>

### Model justification
```{r}
#| echo: false
#| warning: false
#| message: false
model <- lm(pct ~ pollscore + sample_size + numeric_grade, data = clean_data)
summary(model)
```
